Optimization model for multi-product multi-period multi-supplier raw-material selection and composition, and order quantity problem with minimum one-year order quantity contract

### 2023-03-08 Thesis/MethodX/Manuscript/Manuscript.Rmd
sampe tabel parameter

```{r,include=FALSE}
setwd("~/209_ITB/Thesis/MethodX/Manuscript")
```

@@

- $M = \left\{ 1,2,3,4 \right\}$ as the set of weeks on the supply cycle, 
- $N$ as the number of raw materials, 
- $\mathfrak{N}= \left\{ 1,2,...,N \right\}$ as the set of raw-materials,
- $I$ as the number of items,
- $\mathfrak{J} =  \left\{ 1, 2, ..., I  \right\}$ as the number of items,
- $P \bigcup_{j \in M} P_j$ as the set of items to be produced on the planning horizon, where $P_j$ as the set of items to be produced on week $j$.
- For $i \in \mathfrak{J}, k \in \mathfrak{N}$,

@@

__Constraints VI__ are set to fulfill the Policy II.

# Equations

Here is an equation:
$$ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
$$

Here is another:
\begin{align}
  a^2+b^2=c^2.
\end{align}

Inline equations: $\sum_{i = 2}^\infty\{\alpha_i^\beta\}$

# Tables coming from R

Tables can also be generated using R chunks, as shown in Table \ref{tab1} for example.

```{r tab1, echo = TRUE}
knitr::kable(head(mtcars)[,1:4], 
    caption = "\\label{tab1}Caption centered above table"
)
```

>>>>

```{r,include=FALSE}
setwd("~/209_ITB/Thesis/MethodX/Manuscript")

library(dplyr)
```

@@

- $M = \left\{ 1,2,3,4 \right\}$ as the set of weeks on the supply cycle, 
- $N$ as the number of raw materials, 
- $\mathfrak{N}= \left\{ 1,2,...,N \right\}$ as the set of raw-materials,
- $I$ as the number of items,
- $\mathfrak{I} =  \left\{ 1, 2, ..., I  \right\}$ as the number of items,
- $P \bigcup_{j \in M} P_j$ as the set of items to be produced on the planning horizon, where $P_j$ as the set of items to be produced on week $j$.
- For $i \in \mathfrak{I}, k \in \mathfrak{N}$,

@@

__Constraints VI__ are set to fulfill the Policy II. $\forall j \in \hat{M}, \forall i \in P^2_j, k_1, k_2 \in N, k_1 \neq k_2,$

\begin{align}
  (1 - a_{ijk_1}) + (1 - a_{ijk_2}) \geq b_{ijk_1} - b_{ijk_2}
\end{align}

\begin{align}
  (1 - a_{ijk_1}) + (1 - a_{ijk_2}) \geq b_{ijk_2} - b_{ijk_1}
\end{align}

__Constraints VII__ are set to ensure that the level of inventory just after raw material delivery does not exceed the maximum capacity. On the beginning of week 1,

\begin{align}
  \sum_{k \in N} (z_{0k} + \hat{x}_{1k} + z_{1k}) - D_1 \leq maxcap
\end{align}

$\forall j \in \left\{ 2,3,4 \right\},$

\begin{align}
  \sum_{k \in N} (z_{(j-1)k} + \hat{x}_{(j-1)k}) - \sum_{i \in P_j} b_{ijk} g_{ik} + z_jk \leq maxcap
\end{align}

$\forall j \in M,$

\begin{align}
  \sum_{k \in N} (z_{(j-1)k} + \hat{x}_{jk}) - \sum_{i \in P_j} b_{ijk} g_{ik} + z_jk \leq maxcap
\end{align}

__Constraints VIII__ are set to ensure that the level of inventory at the end of each week must be greater than or equal to the safety stock. $\forall j \in M, \forall k \in P,$

\begin{align}
  z_{jk} \geq ss
\end{align}

### Objective function

We define the objective function as the sum of the holding cost, the purchase cost, and a function for accommodating the minimum one-year order quantity contracts.

The level of inventory of raw-material $k$ during one week can be seen in figure 3.

```{r out.width="70%",fig.align='center',echo=FALSE,fig.cap="Illustration for inventory cost calculation"}
knitr::include_graphics("inventory.jpg")
```

So that the holding cost can be given as:

$$
\frac{1}{2} hc \sum_{j \in \mathfrak{M}} \sum_{k \in \mathfrak{N}} (z_{(j-1)k} + z_{jk} + \hat{x}_{jk})
$$

Meanwhile the purchase cost can be given as:

$$
  \sum_{k \in \mathfrak{N}} c_k x_k
$$

We consider another function in the objective function, which is created to accommodate the one-year minimum order quantity contracts.

Constraints I - VIII concern fulfillment of the minimum one-month order quantity contract, the monthly demand,   warehouse capacity constraint, safety stock constraint, and raw material composition requirements. Meanwhile, the one-year minimum order quantity contract is quite difficult to be expressed as a constraint in the optimization model that has a one-month-long planning horizon.

Therefore, we accommodate the yearly purchase contract which we represent as a part of the objective function of our optimization problem. To fulfill the one-year minimum order quantity contracts, we define a penalty function:

$$
  - \sum_{k \in \mathfrak{N}} \alpha_k mo_k x_k
$$

where for $k \in \mathfrak{N}, \alpha_k$ is multiplier constants that will be discussed later. By denoting $\bar{x}$ as the vector with elements $x_k$ and $\hat{x}_{jk},$ and $\bar{z}$ as the vector with elements $z_{jk}$ the objective function of our optimization model is then can be written as:

$$
  F(\bar{x},\bar{z}) = \frac{1}{2} hc \sum_{j \in \mathfrak{M}} \sum_{k \in \mathfrak{N}} (z_{(j-1)k} + z_{jk} + \hat{x}_{jk}) + \sum_{k \in \mathfrak{N}} c_k x_k - \sum_{k \in \mathfrak{N}} \alpha_k mo_k x_k
$$

### Optimization model

The optimization model for supplier selection, order allocation, and raw material composition can be written as a mixed integer linear programming:

$$
\begin{matrix}
minimize & F(\bar{x},\bar{z}) \\
subject \space to & Constraint \space I-VIII \\
 & x_k, \hat{x}_{jk}, z_{jk} \in \mathbb{Z}^+, y_k, a_{ijk} \in \left\{0,1 \right\}, 0 \leq b_{ijk} \leq 1
\end{matrix}
$$

where the set of __Constraints I__ up to __Constraints VIII__ are given by equations (1) - (15).

# Results

In this section, we give an example of the solution of the optimization model we derived in the previous section. In this example, we consider an instant where $N=6$ and $I=51,$ so that we have 2508 decision variables.

## Parameters values

The following tables show the matrix of raw-material flexibility of all items.

```{r,echo=FALSE,message=FALSE,warning=FALSE}
rm(list=ls())

library(readxl)
library(kableExtra)

df = read_excel("~/209_ITB/Thesis/Overleaf Version/data input.xlsx",sheet = "matriks gula x produk")
df[is.na(df)] = 0
colnames(df)[2:7] = 1:6
df[1:25,] %>% 
  rename(item = code_product) %>% 
  knitr::kable(caption = "the flexibility matrix of items 1-25") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  add_header_above(c(" " = 1,"Raw material" = 6))
```
\pagebreak

```{r,echo=FALSE,message=FALSE,warning=FALSE}
df[26:51,] %>% 
  rename(item = code_product) %>% 
  knitr::kable(caption = "the flexibility matrix of items 26-51") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  add_header_above(c(" " = 1,"Raw material" = 6))
```

Next, we present the instant of the total raw material demands during a planning horizon.

```{r,echo=FALSE,message=FALSE,warning=FALSE}
rm(list=ls())

df = read_excel("~/209_ITB/Thesis/Overleaf Version/data input.xlsx",sheet = "matriks produk x minggu")
colnames(df)[2:5] = paste0("week ",1:4)
df[1:11,] %>% 
  rename(item = code_product) %>% 
  knitr::kable(caption = "the flexibility matrix of items 1-11") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  add_header_above(c(" " = 1,"raw -material demand (in kg)" = 4))
```

```{r,echo=FALSE,message=FALSE,warning=FALSE}
df[12:51,] %>% 
  rename(item = code_product) %>% 
  knitr::kable(caption = "the flexibility matrix of items 12-51") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  add_header_above(c(" " = 1,"raw -material demand (in kg)" = 4))
```

We can see that items 5 and 36 do not have to be produced during this planning horizon. We also can see that most items have to be produced only in to or three weeks of this planning horizon, with varying demand.

The others parameters values are given in the following table.

### 2023-03-08 Thesis/MethodX/Manuscript/Manuscript.tex
sampe tabel parameter

% Pandoc syntax highlighting
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

@@

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

@@

@@

\begin{itemize}
\tightlist
\item
  \(M = \left\{ 1,2,3,4 \right\}\) as the set of weeks on the supply
  cycle,
\item
  \(N\) as the number of raw materials,
\item
  \(\mathfrak{N}= \left\{ 1,2,...,N \right\}\) as the set of
  raw-materials,
\item
  \(I\) as the number of items,
\item
  \(\mathfrak{J} = \left\{ 1, 2, ..., I \right\}\) as the number of
  items,
\item
  \(P \bigcup_{j \in M} P_j\) as the set of items to be produced on the
  planning horizon, where \(P_j\) as the set of items to be produced on
  week \(j\).
\item
  For \(i \in \mathfrak{J}, k \in \mathfrak{N}\),
\end{itemize}

@@

\hypertarget{equations}{%
\section{Equations}\label{equations}}

Here is an equation: \[ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
\]

Here is another: \begin{align}
  a^2+b^2=c^2.
\end{align}

Inline equations: \(\sum_{i = 2}^\infty\{\alpha_i^\beta\}\)

\hypertarget{tables-coming-from-r}{%
\section{Tables coming from R}\label{tables-coming-from-r}}

Tables can also be generated using R chunks, as shown in Table
\ref{tab1} for example.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}\FunctionTok{head}\NormalTok{(mtcars)[,}\DecValTok{1}\SpecialCharTok{:}\DecValTok{4}\NormalTok{], }
    \AttributeTok{caption =} \StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{label\{tab1\}Caption centered above table"}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}lrrrr@{}}
\caption{\label{tab1}Caption centered above table}\tabularnewline
\toprule()
& mpg & cyl & disp & hp \\
\midrule()
\endfirsthead
\toprule()
& mpg & cyl & disp & hp \\
\midrule()
\endhead
Mazda RX4 & 21.0 & 6 & 160 & 110 \\
Mazda RX4 Wag & 21.0 & 6 & 160 & 110 \\
Datsun 710 & 22.8 & 4 & 108 & 93 \\
Hornet 4 Drive & 21.4 & 6 & 258 & 110 \\
Hornet Sportabout & 18.7 & 8 & 360 & 175 \\
Valiant & 18.1 & 6 & 225 & 105 \\
\bottomrule()
\end{longtable}

>>>>

@@

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\begin{itemize}
\tightlist
\item
  \(M = \left\{ 1,2,3,4 \right\}\) as the set of weeks on the supply
  cycle,
\item
  \(N\) as the number of raw materials,
\item
  \(\mathfrak{N}= \left\{ 1,2,...,N \right\}\) as the set of
  raw-materials,
\item
  \(I\) as the number of items,
\item
  \(\mathfrak{I} = \left\{ 1, 2, ..., I \right\}\) as the number of
  items,
\item
  \(P \bigcup_{j \in M} P_j\) as the set of items to be produced on the
  planning horizon, where \(P_j\) as the set of items to be produced on
  week \(j\).
\item
  For \(i \in \mathfrak{I}, k \in \mathfrak{N}\),
\end{itemize}

@@

\textbf{Constraints VI} are set to fulfill the Policy II.
\(\forall j \in \hat{M}, \forall i \in P^2_j, k_1, k_2 \in N, k_1 \neq k_2,\)

\begin{align}
  (1 - a_{ijk_1}) + (1 - a_{ijk_2}) \geq b_{ijk_1} - b_{ijk_2}
\end{align}

\begin{align}
  (1 - a_{ijk_1}) + (1 - a_{ijk_2}) \geq b_{ijk_2} - b_{ijk_1}
\end{align}

\textbf{Constraints VII} are set to ensure that the level of inventory
just after raw material delivery does not exceed the maximum capacity.
On the beginning of week 1,

\begin{align}
  \sum_{k \in N} (z_{0k} + \hat{x}_{1k} + z_{1k}) - D_1 \leq maxcap
\end{align}

\(\forall j \in \left\{ 2,3,4 \right\},\)

\begin{align}
  \sum_{k \in N} (z_{(j-1)k} + \hat{x}_{(j-1)k}) - \sum_{i \in P_j} b_{ijk} g_{ik} + z_jk \leq maxcap
\end{align}

\(\forall j \in M,\)

\begin{align}
  \sum_{k \in N} (z_{(j-1)k} + \hat{x}_{jk}) - \sum_{i \in P_j} b_{ijk} g_{ik} + z_jk \leq maxcap
\end{align}

\textbf{Constraints VIII} are set to ensure that the level of inventory
at the end of each week must be greater than or equal to the safety
stock. \(\forall j \in M, \forall k \in P,\)

\begin{align}
  z_{jk} \geq ss
\end{align}

\hypertarget{objective-function}{%
\subsubsection{Objective function}\label{objective-function}}

We define the objective function as the sum of the holding cost, the
purchase cost, and a function for accommodating the minimum one-year
order quantity contracts.

The level of inventory of raw-material \(k\) during one week can be seen
in figure 3.

{\centering \includegraphics[width=0.7\linewidth]{inventory}

\caption{Illustration for inventory cost calculation}\label{fig:unnamed-chunk-4}
\end{figure}

So that the holding cost can be given as:

\[
\frac{1}{2} hc \sum_{j \in \mathfrak{M}} \sum_{k \in \mathfrak{N}} (z_{(j-1)k} + z_{jk} + \hat{x}_{jk})
\]

Meanwhile the purchase cost can be given as:

\[
  \sum_{k \in \mathfrak{N}} c_k x_k
\]

We consider another function in the objective function, which is created
to accommodate the one-year minimum order quantity contracts.

Constraints I - VIII concern fulfillment of the minimum one-month order
quantity contract, the monthly demand, warehouse capacity constraint,
safety stock constraint, and raw material composition requirements.
Meanwhile, the one-year minimum order quantity contract is quite
difficult to be expressed as a constraint in the optimization model that
has a one-month-long planning horizon.

Therefore, we accommodate the yearly purchase contract which we
represent as a part of the objective function of our optimization
problem. To fulfill the one-year minimum order quantity contracts, we
define a penalty function:

\[
  - \sum_{k \in \mathfrak{N}} \alpha_k mo_k x_k
\]

where for \(k \in \mathfrak{N}, \alpha_k\) is multiplier constants that
will be discussed later. By denoting \(\bar{x}\) as the vector with
elements \(x_k\) and \(\hat{x}_{jk},\) and \(\bar{z}\) as the vector
with elements \(z_{jk}\) the objective function of our optimization
model is then can be written as:

\[
  F(\bar{x},\bar{z}) = \frac{1}{2} hc \sum_{j \in \mathfrak{M}} \sum_{k \in \mathfrak{N}} (z_{(j-1)k} + z_{jk} + \hat{x}_{jk}) + \sum_{k \in \mathfrak{N}} c_k x_k - \sum_{k \in \mathfrak{N}} \alpha_k mo_k x_k
\]

\hypertarget{optimization-model}{%
\subsubsection{Optimization model}\label{optimization-model}}

The optimization model for supplier selection, order allocation, and raw
material composition can be written as a mixed integer linear
programming:

\[
\begin{matrix}
minimize & F(\bar{x},\bar{z}) \\
subject \space to & Constraint \space I-VIII \\
 & x_k, \hat{x}_{jk}, z_{jk} \in \mathbb{Z}^+, y_k, a_{ijk} \in \left\{0,1 \right\}, 0 \leq b_{ijk} \leq 1
\end{matrix}
\]

where the set of \textbf{Constraints I} up to \textbf{Constraints VIII}
are given by equations (1) - (15).

\hypertarget{results}{%
\section{Results}\label{results}}

In this section, we give an example of the solution of the optimization
model we derived in the previous section. In this example, we consider
an instant where \(N=6\) and \(I=51,\) so that we have 2508 decision
variables.

\hypertarget{parameters-values}{%
\subsection{Parameters values}\label{parameters-values}}

The following tables show the matrix of raw-material flexibility of all
items.

\begin{table}[!h]

\caption{\label{tab:unnamed-chunk-5}the flexibility matrix of items 1-25}
\centering
\begin{tabular}[t]{r|r|r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{6}{c}{Raw material} \\
\cline{2-7}
item & 1 & 2 & 3 & 4 & 5 & 6\\
\hline
1 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
2 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
3 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
4 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
5 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
6 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
7 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
8 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
9 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
10 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
11 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
12 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
13 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
14 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
15 & 1 & 0 & 0 & 1 & 0 & 0\\
\hline
16 & 1 & 0 & 0 & 1 & 0 & 0\\
\hline
17 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
18 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
19 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
20 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
21 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
22 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
23 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
24 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
25 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
\end{tabular}
\end{table}
\pagebreak

\begin{table}[!h]

\caption{\label{tab:unnamed-chunk-6}the flexibility matrix of items 26-51}
\centering
\begin{tabular}[t]{r|r|r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{6}{c}{Raw material} \\
\cline{2-7}
item & 1 & 2 & 3 & 4 & 5 & 6\\
\hline
26 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
27 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
28 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
29 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
30 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
31 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
32 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
33 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
34 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
35 & 1 & 1 & 0 & 1 & 0 & 1\\
\hline
36 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
37 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
38 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
39 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
40 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
41 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
42 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
43 & 1 & 1 & 1 & 1 & 0 & 1\\
\hline
44 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
45 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
46 & 1 & 1 & 0 & 1 & 0 & 1\\
\hline
47 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
48 & 1 & 1 & 1 & 1 & 1 & 1\\
\hline
49 & 0 & 0 & 0 & 1 & 0 & 0\\
\hline
50 & 0 & 0 & 0 & 1 & 0 & 0\\
\hline
51 & 1 & 1 & 0 & 1 & 0 & 0\\
\hline
\end{tabular}
\end{table}

Next, we present the instant of the total raw material demands during a
planning horizon.

\begin{table}[!h]

\caption{\label{tab:unnamed-chunk-7}the flexibility matrix of items 1-11}
\centering
\begin{tabular}[t]{r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{4}{c}{raw -material demand (in kg)} \\
\cline{2-5}
item & week 1 & week 2 & week 3 & week 4\\
\hline
1 & 2555.1 & 2555.1 & 0 & 10220.4\\
\hline
2 & 0.0 & 4300.0 & 8600 & 0.0\\
\hline
3 & 0.0 & 0.0 & 0 & 1800.0\\
\hline
4 & 0.0 & 495.0 & 0 & 0.0\\
\hline
5 & 0.0 & 0.0 & 0 & 0.0\\
\hline
6 & 3150.0 & 0.0 & 6300 & 0.0\\
\hline
7 & 0.0 & 1050.0 & 0 & 350.0\\
\hline
8 & 1650.0 & 0.0 & 0 & 2200.0\\
\hline
9 & 2080.0 & 1560.0 & 1040 & 0.0\\
\hline
10 & 0.0 & 1280.0 & 0 & 0.0\\
\hline
11 & 0.0 & 0.0 & 4200 & 0.0\\
\hline
\end{tabular}
\end{table}

\begin{table}[!h]

\caption{\label{tab:unnamed-chunk-8}the flexibility matrix of items 12-51}
\centering
\begin{tabular}[t]{r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{4}{c}{raw -material demand (in kg)} \\
\cline{2-5}
item & week 1 & week 2 & week 3 & week 4\\
\hline
12 & 0 & 2700 & 0 & 0\\
\hline
13 & 350 & 350 & 0 & 0\\
\hline
14 & 0 & 300 & 500 & 200\\
\hline
15 & 85 & 0 & 0 & 0\\
\hline
16 & 110 & 165 & 0 & 0\\
\hline
17 & 0 & 0 & 17400 & 17400\\
\hline
18 & 74050 & 222150 & 14800 & 0\\
\hline
19 & 0 & 11605 & 0 & 0\\
\hline
20 & 12750 & 0 & 0 & 0\\
\hline
21 & 3500 & 0 & 14000 & 14000\\
\hline
22 & 42100 & 0 & 10550 & 0\\
\hline
23 & 0 & 0 & 5600 & 11200\\
\hline
24 & 5400 & 5400 & 0 & 5400\\
\hline
25 & 1350 & 2250 & 0 & 0\\
\hline
26 & 0 & 32400 & 43200 & 0\\
\hline
27 & 10350 & 31050 & 0 & 0\\
\hline
28 & 118200 & 0 & 0 & 0\\
\hline
29 & 3330 & 4995 & 0 & 0\\
\hline
30 & 0 & 1950 & 0 & 5850\\
\hline
31 & 0 & 6300 & 6300 & 0\\
\hline
32 & 2310 & 3465 & 0 & 0\\
\hline
33 & 0 & 2500 & 0 & 0\\
\hline
34 & 0 & 0 & 20850 & 0\\
\hline
35 & 12150 & 0 & 0 & 0\\
\hline
36 & 0 & 0 & 0 & 0\\
\hline
37 & 12750 & 12750 & 8500 & 8500\\
\hline
38 & 1550 & 3100 & 0 & 0\\
\hline
39 & 0 & 10600 & 5300 & 21200\\
\hline
40 & 0 & 0 & 10450 & 20900\\
\hline
41 & 9625 & 0 & 1375 & 1375\\
\hline
42 & 0 & 0 & 3080 & 0\\
\hline
43 & 0 & 2250 & 450 & 2250\\
\hline
44 & 0 & 0 & 14100 & 0\\
\hline
45 & 6700 & 13400 & 10050 & 6700\\
\hline
46 & 6500 & 13000 & 0 & 0\\
\hline
47 & 26200 & 13100 & 0 & 0\\
\hline
48 & 12000 & 8000 & 0 & 12000\\
\hline
49 & 0 & 126 & 0 & 0\\
\hline
50 & 1323 & 0 & 3969 & 0\\
\hline
51 & 1170 & 1170 & 0 & 780\\
\hline
\end{tabular}
\end{table}

We can see that items 5 and 36 do not have to be produced during this
planning horizon. We also can see that most items have to be produced
only in to or three weeks of this planning horizon, with varying demand.

The others parameters values are given in the following table.
